Co-citations in context

### 2019-06-04 cocit_r.tex
Update cocit_r.tex

Another possible symptom of model misspecification is to find that the citations associated with an article under random sampling do not match with the observed disciplinary makeup of citation in practice. \emph{More needed here}  Here is Sitaram's study:

>>>>

Another possible symptom of model misspecification is that random sampling of citations associated with an article do not match with the observed disciplinary makeup of citation in practice. \emph{More needed here}  Here is Sitaram's study:
